\documentclass[conference]{IEEEtran}
\usepackage{cite}
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
 \fi
\usepackage[cmex10]{amsmath}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{caption} 
\captionsetup[table]{skip=10pt}
\usetikzlibrary{matrix,chains,positioning,decorations.pathreplacing,arrows}
\usepackage{amsmath}
\usepackage{float}
\usepackage{booktabs}
\IEEEoverridecommandlockouts
%s\hyphenation{op-tical net-works semi-conduc-tor}
\title{Movie Recommendations Using \\ Low-dimensional Codes  \\ and User Specified \\ Feature Relevance}
\author{
\IEEEauthorblockN{Christopher Curro, David Katz, Harrizon Zhao}
\IEEEauthorblockA{The Cooper Union\\
Electrical Engineering
}
}
\begin{document}
\maketitle
\global\csname @topnum\endcsname 0
\global\csname @botnum\endcsname 0
\begin{abstract} 

We present a movie recommendation system that finds a weighted set of nearest
neighbors to an arbitrary desired movie based on user specified interests in a
latent space learned by an autoencoder. We learn a low-dimensional
representation to make recommendations in from a much larger feature space
consisting of approximately one thousand tags and their relevancies to about
ten thousand movies. 

\end{abstract} 
\section{Introduction} 

Movie recommendation is complex task that generally involves high dimensional
feature spaces; a common approach today is the collaborative filtering
approach \cite{ekstrand2011collaborative,good1999combining,koren2009matrix}.
The collaborative filtering approach is powerful because successfully reduces
a complex high-dimensional feature space into a rich low-dimensional latent
space. We aim to present an alternative approach to generating a rich low-dimensional latent space capable of producing high quality movie
recommendations based on nearest neighbor approach where the queried sample is
determined by user input. We work with the dataset created by Vig et al.
\cite{vig2012tag}. This dataset provides a approximately ten thousand movies each with relevance weightings for approximately one thousand tags.  We labeled each of our latent features in a human understandable manner.  We also provided users with the ability to adjust both the target value and the relevance of each of these features at each query.

\subsection{Autoencoders}
\input{autoencIntro}
\subsection{Nearest Neighbors Recommendations}
\input{nnIntro}
\section{System Description}

\subsection{Autoencoder}
\input{autoencSys}
\subsection{Feature Tagging}
\input{featuretagSys}
\subsection{Interface}
\input{interfaceSys}
\subsection{Recommendations}
\input{nnSys}

\section{Results}
No real metric exists other than user engagement.

We keep logs of all of the queries performed.  These logs of real user data could serve as a valuable dataset for maximizing the efficiency of an ANN index.

\section{Conclusion}
marshmellow fluff

% \IEEEpeerreviewmaketitle

\raggedright
\bibliographystyle{IEEEtran}
\bibliography{bib}

\end{document}
